---
title: "Day 4- Exploring Data"
author: "Kristine Duarte"
format: html
editor: visual
---

```{r}
#| warning: false
#| echo: false

library(tidyverse)
library(palmerpenguins)
library(GGally) #install.packages("GGally")
library(skimr) #install.packages("skimr")

#if packages don't work, remember to install packages in the consol and to use ""
```

#\| warning: false

#\| echo: false echo means don't show me the code, but it will show the output

putting them in the code (above) in Quarto can make this not show up in the rendered document

## Exploratory Data Viz

View() in consol will bring up the data set so you can look at it

Check out your data a bit:

```{r}
#| include: false

#Tell me the column names
names(penguins)

#What are the dimensions?
dim(penguins)

#Can you show me the first six lines?
head(penguins)

#Can you show me the last six lines? 
tail(penguins)
```

Let's make some Data Viz!

```{r}
skim(penguins)

#skim is great way to see overview of the data, including histogram of distribution
```

```{r}
#| warning: false
GGally::ggpairs(penguins)
```

##Jitterplot- show a lot of the data

Flipper length by species

```{r}
#| echo: false
ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) + geom_jitter(width = 0.2, 
                                                                               alpha = 0.5, height = 0,
                                                                               aes(color = species)) + 
  geom_boxplot(fill = NA) +
  theme_light() + scale_color_manual(values = c("darkorchid4", "cyan4", "goldenrod")) + 
  labs(x = "Penguin Species", y = "Flipper length (mm)", legend = "Species")
```

Exploratory Histogram

```{r}
ggplot(data = penguins, aes(x = bill_length_mm)) + 
  geom_histogram(aes(fill = species), color = "magenta") +  facet_wrap(~species, ncol = 1)
  
```
